---
title: "Developing Data Products Week 4 Project - Shiny"
author: "Sang Cho"
date: "July 23, 2017"
output: slidy_presentation
---

```{r setup,include=FALSE,eval=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## State and Local Tax Rate by State
- Data Source:  "https://files.taxfoundation.org/20170131121743/TaxFoundation-FF539.pdf"
- Illustrates the average combined (state + local) tax rate by state

## Data Processing

- The data processing is included in the server.R File

```{r, echo=TRUE,messages=FALSE,warning=FALSE,results="hide",eval=FALSE}
data.tax <- as.data.frame(read.table(file="state tax.txt",sep=',',header=TRUE,na.strings=c(" ","NA","-")))
avg.combined.tax <- data.tax[,c("State","Combined_Rate")]
avg.combined.tax$Combined_Rate <- as.numeric(sub("%","",avg.combined.tax$Combined_Rate))/100
avg.combined.tax[51,2] <- 0.0575

```

## ui.R
- Code for ui.R in order to control what to be displayed as output

```{r,eval=FALSE}
library(shiny)
shinyUI(fluidPage(
  titlePanel("The average combined (state + local) tax rate by state"),
  sidebarLayout(
    sidebarPanel(
       h1("Move the slider to control the range of tax rates"),
       sliderInput("cbr",
                   "Combined State and Local Tax Rate:",
                   min = 0,
                   max = 0.1,
                   value = c(0.02, 0.09)),
     submitButton("Submit")
    ),
    mainPanel(
       h2("Histogram of the average combined tax rate by state"),
       plotOutput("Histogram")
  )
)
)
)
```

## Server.R File
- The output is to display the histogram conditionally based on setting the ranges of combined tax rate

```{r, echo=TRUE,messages=FALSE,eval=FALSE}
shinyServer(function(input, output) {
    subdata <- reactive({
      minY <- input$cbr[1]
      maxY <- input$cbr[2]
      subset(avg.combined.tax,Combined_Rate >= minY & Combined_Rate <= maxY)
    })
    output$Histogram <- renderPlot({
    hist(subdata()$Combined_Rate, col = 'darkgray', border = 'white')
    })
  })
```

## Link to github and webapp
-  Link to Github:  https://github.com/openended111/DDPShiny
-  Link to Shiny App:  https://openended111.shinyapps.io/ddp_project/

